A publishing infrastructure for AI-assisted academic authoring

### 2023-07-11 latex/manuscript.tex
split conclusions into discussion and conclusions
rename the methods and results section

\hypertarget{implementing-ai-based-revision-into-the-manubot-publishing-ecosystem}{%
\subsection{Implementing AI-based revision into the Manubot publishing ecosystem}\label{implementing-ai-based-revision-into-the-manubot-publishing-ecosystem}}

@@

\hypertarget{sec:results}{%
\subsection{Observations of AI-based revisions}\label{sec:results}}

@@

>>>>

\hypertarget{materials-and-methods}{%
\subsection{Materials and Methods}\label{materials-and-methods}}

@@

\hypertarget{sec:results}{%
\subsection{Results}\label{sec:results}}

@@

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}
